Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
TDD: what's it?

In other programming language communities,
behavior driven development (BDD) is getting much attention, and is
slowly replacing test driven development (TDD).
In BDD, test code is written with specification terminology.
In other words, specifications can be used for automatic testing.

In this paper, we explore how to apply BDD to Haskell.
BDD approaches
TDD and acceptance test-driven development (ATDD)
with a new terminology and mindset. 
For the purpose of this paper we only focus on the TDD aspect of BDD.

>>>>

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to reqire more details and drive the
implementation closer to the desired goal.  Rinse and repeat.  BDD
includes TDD, amongst other software development methodologies, but
with a terminology and mindset  shifted towards specification instead
of testing.  In BDD, specifications can be used for automatic testing.

In this paper, we explore how to apply BDD to Haskell.
For the purpose of this paper we only focus on the TDD aspect of BDD.
